\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{pifont} % \ding{51} = check, \ding{55} = cross (coverage table)

\title{EuroPriv-Bench: A Unified Pan-European De-identification Benchmark\\
       with Privacy-Utility Metrics}
\author{KlusAI}
\date{2026}

\begin{document}
\maketitle

\begin{abstract}
% POSITIONING DISCIPLINE: claim "first UNIFIED", never bare "first". Cite + subsume prior art.
Privacy-focused NLP for European languages is served by fragmented resources: the Text
Anonymization Benchmark~\cite{pilan2022tab} provides privacy-utility metrics but is
English- and legal-only; AI4Privacy~\cite{ai4privacy_openpii} offers cross-lingual European
\emph{detection} data without re-identification metrics; MAPA~\cite{mapa_toolkit} spans 24 EU
languages and both legal and clinical text but is a detection toolkit, not a leaderboard; and
MultiGraSCCo~\cite{multigrascco2026} is multilingual but clinical-only and translation-based.
Concurrent and independent work, RAT-Bench~\cite{ratbench2026}, contributes a hosted
re-identification-risk benchmark but is built on U.S. demographics
(English/Spanish/Chinese), with no legal text and no GDPR-aligned taxonomy.
Meanwhile the privacy-filter lineage~\cite{openai_privacy_filter_2026,openmed_privacy_filter_ml_2026}
and recent PII models such as GLiNER2-PII~\cite{gliner2pii2026} ship strong models with \emph{no}
standardized European evaluation, and a 2025 survey of the field flags exactly this
missing standardized multilingual benchmark~\cite{deusser2025survey}. We introduce
\textbf{EuroPriv-Bench}, the first unified, openly-licensed leaderboard for European
cross-lingual legal \emph{and} clinical de-identification with a harmonized GDPR-aligned entity
taxonomy and a re-identification-risk metric. It unifies (a)~European cross-lingual breadth,
(b)~both legal and clinical domains, (c)~one harmonized GDPR-aligned taxonomy, and
(d)~re-identification-risk and privacy-utility metrics in (e)~a single reproducible,
openly-licensed, leaderboard-style suite. We build \emph{on top of} the prior art, re-using their
splits and metrics where applicable, and report a baseline study ranking
\texttt{openai/privacy-filter}, OpenMed, \texttt{tabularisai}, GLiNER, and Presidio.
\end{abstract}

\section{Introduction}
% Motivate the unified gap; state the kill/pivot reasoning resolved in Phase 0.
EuroPriv-Bench is, to our knowledge, the first unified, openly-licensed leaderboard for European
cross-lingual legal \emph{and} clinical de-identification with a harmonized GDPR-aligned entity
taxonomy and a re-identification-risk metric. We deliberately claim ``first \emph{unified}'' rather
than ``first'': each constituent capability exists in prior art, but no prior artifact combines all
of them in one reproducible suite (Section~\ref{sec:related}).

\section{The Harmonized KP Taxonomy}
% GDPR Art. 4/9 mapping; direct vs. quasi-identifier; crosswalk to OpenAI/HIPAA/MAPA/AI4Privacy.

\section{Benchmark Construction}
% Cleanly-licensed sources only; held-out gold; synthetic train kept separate.

\section{Metrics}
% Entity F1 / recall-weighted F2; re-identification risk; privacy-utility; leakage (MIA).

\section{Baseline Study}
% Leaderboard table ingested from europriv-bench/baselines/leaderboard.json.

\section{Related Work}
\label{sec:related}
% TAB, AI4Privacy, MAPA, MultiGraSCCo, MEDDOCAN, RAT-Bench, GLiNER2-PII/SPY,
% MedPriv-Bench, PrivaCI-Bench, PIIBench.
We position EuroPriv-Bench against the closest prior and concurrent artifacts along six axes:
(a)~EU cross-lingual coverage, (b)~legal text, (c)~clinical text, (d)~a harmonized GDPR-aligned
entity taxonomy, (e)~a re-identification-risk metric, and an open, reproducible leaderboard.
Table~\ref{tab:related} summarizes coverage. Every prior artifact is missing at least two of these
axes; EuroPriv-Bench is the first to fill all of them in a single suite.

The closest EU-breadth, dual-domain prior art is MAPA~\cite{mapa_toolkit} (24 EU languages, legal
\emph{and} clinical), but it is a detection toolkit with no re-identification metric and no open
leaderboard. The legal-domain re-identification lineage is anchored by TAB~\cite{pilan2022tab},
which pairs a privacy-utility / re-identification framing with legal text but is English-only.
AI4Privacy~\cite{ai4privacy_openpii} contributes cross-lingual European detection data without a
re-identification metric or a GDPR-aligned taxonomy. MultiGraSCCo~\cite{multigrascco2026} is
multilingual but clinical-only and translation-based. MEDDOCAN~\cite{meddocan2019} is a
clinical de-identification track but Spanish-only. EuroPriv-Bench is best understood as the
unification of what MAPA (EU breadth + dual domain) and TAB (legal text + re-identification
metric) each establish in isolation, under one harmonized GDPR-aligned taxonomy.

RAT-Bench~\cite{ratbench2026} is concurrent and independent work: a 2026 hosted
re-identification-risk leaderboard. It is complementary rather than overlapping --- it is built on
U.S. demographic statistics over English, Spanish, and Chinese, contains no legal text, and uses no
GDPR-aligned taxonomy, so it does not address the European legal/clinical de-identification setting
EuroPriv-Bench targets. Recent PII models and corpora are similarly partial: GLiNER2-PII and the SPY
benchmark~\cite{gliner2pii2026,spy2025} provide a strong multilingual PII model and synthetic
evaluation but no re-identification metric or EU legal/clinical framing;
MedPriv-Bench~\cite{medprivbench2026} is a clinical-only LLM-QA privacy-utility benchmark;
PrivaCI-Bench~\cite{privacibench2025} evaluates contextual integrity and legal compliance rather than
span-level de-identification; and PIIBench~\cite{piibench2026} consolidates ten public PII datasets
for detection only. A 2025 survey of text anonymization~\cite{deusser2025survey} explicitly flags
the absence of a standardized multilingual de-identification benchmark --- the gap EuroPriv-Bench
is built to close.

\begin{table}[t]
\centering
\small
\caption{Coverage of related and concurrent artifacts. Columns: (a)~EU cross-lingual,
(b)~legal, (c)~clinical, (d)~harmonized GDPR taxonomy, (e)~re-identification-risk metric,
(f)~open reproducible leaderboard. Every prior row is missing $\geq 2$ columns; only
EuroPriv-Bench fills all six.}
\label{tab:related}
\begin{tabular}{lcccccc}
\toprule
Artifact & (a) EU x-ling & (b) legal & (c) clinical & (d) GDPR tax. & (e) re-id metric & (f) leaderboard \\
\midrule
TAB~\cite{pilan2022tab}                 & \ding{55} & \ding{51} & \ding{55} & \ding{55} & \ding{51} & \ding{55} \\
AI4Privacy~\cite{ai4privacy_openpii}    & \ding{51} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} \\
MAPA~\cite{mapa_toolkit}                & \ding{51} & \ding{51} & \ding{51} & \ding{55} & \ding{55} & \ding{55} \\
MultiGraSCCo~\cite{multigrascco2026}    & \ding{51} & \ding{55} & \ding{51} & \ding{55} & \ding{55} & \ding{55} \\
MEDDOCAN~\cite{meddocan2019}            & \ding{55} & \ding{55} & \ding{51} & \ding{55} & \ding{55} & \ding{55} \\
RAT-Bench~\cite{ratbench2026}           & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{51} & \ding{51} \\
GLiNER2-PII / SPY~\cite{gliner2pii2026,spy2025} & \ding{51} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} \\
MedPriv-Bench~\cite{medprivbench2026}   & \ding{55} & \ding{55} & \ding{51} & \ding{55} & \ding{55} & \ding{55} \\
PrivaCI-Bench~\cite{privacibench2025}   & \ding{55} & \ding{51} & \ding{55} & \ding{55} & \ding{55} & \ding{51} \\
PIIBench~\cite{piibench2026}            & \ding{51} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} \\
\midrule
\textbf{EuroPriv-Bench (ours)}          & \ding{51} & \ding{51} & \ding{51} & \ding{51} & \ding{51} & \ding{51} \\
\bottomrule
\end{tabular}
\end{table}

\bibliographystyle{plain}
\bibliography{../../shared/klusai}

\end{document}
